\subsection{Purpose}
\label{intro:purpose}
This document specifies the Software Requirements Specification for the Task Management for Tomboy Project. 
It describes scope of the system, both functional and non-functional requirements for the software, design constraints and system interfaces.


\subsection{Scope}
\label{intro:scope}
The project TaskList is an Addin for Tomboy that will provide the functionality of writing simple task lists. The user should be able to create, manage and edit those lists within individual tomboy notes. 
There should be the possibility to enhance simple task list entries with optional arguments such as due dates, priority etc, create subtasks and list the contents of some collection of tasks or tasklists.  

The user should be able to use tomboy with the Addin intuitively for daily usage. The Addin itself will be fully integrated into Tomboy and therefore ...

\textit{Identify by name the software product to be produced (e.g., Host DBMS, Report Generator, etc.)
Explain what the product will and will not do
Describe application of the software: goals and benefits
Establish relation with higher-level system requirements if any}

\subsection{Definitions, acronyms and abbreviations}
\label{intro:definitions}

\begin{objects}
	% Make sure to maintain alphabetical order
	\object{CLI}{Common Language Infrastructure}
	\object{C\#}{C-Sharp}
	\object{GTK}{GIMP ToolKit}
	\object{GTK\#}{Gtk Sharp}
	\object{GUI}{Graphical User Interface}
\end{objects}


\subsection{Glossary}
\label{intro:glossary}

\begin{objects}
	% Make sure to maintain alphabetical order
	\object{Addin}{An extension for a particular Product.}
	\object{Cross Platform}{Attribute conferred to computer software which is implemented and inter-operates on multiple computer platforms.}
	\object{C-Sharp}{Programming Language for the CLI Standard.}
	\object{GIMP ToolKit}{A cross platform widget library for creating GUIs.}
	\object{GTK Sharp}{GTK Language Bindings for C\#}
	\object{Mono}{Cross Platform .NET Compatible Open Source implementation of the CLI Standard.}
	\object{Task}{An activity.}
	\object{Tomboy}{A desktop note-taking application for Linux and Unix written in C\# using Mono.}
	\object{User}{Any Person who uses the Program.}
	\object{.NET Framework}{Microsofts Implementation of the CLI Standard.}
\end{objects}



\subsection{References}
\label{intro:references}

\subsection{Overview}
\label{intro:overview}
