\section{Open Issues}
\label{issues}

This section sums up issues encountered during the process of the project that could not yet be solved.
Some of them were introduced just before submission and therefore not discovered until after.

\begin{itemize}
\item Unit test failure for wrong locale

  If the test is run in a locale that uses a different format than the one hard coded in the test XMLs, the corresponding test (LoadingDueDates, FindOverdueTasks) will fail.

\item Gtk\# assertion failure upon deleting note

  When deleting a note containing task lists with tasks, a Gtk\# assertion failure may happen.
  However, there is no incidence that this leads to further errors/exceptions.

\item Tomboy crashes for fresh notes with due date/priority

  If the first thing one does after start up is the creation of a new note with a task list and a due date or priority is added, then Tomboy may crash. This does not happen if one tries this to a existing note (even if no task list is inside it), or if other notes (it does not matter whether they contain a task list or not) are opened first. 
  
This, and the fact that this bug was introduced in some of the latest commits, made us not discover the bug in time before the submission of our code. Otherwise, it could have probably be fixed without too much effort.

\item Undo/Redo mechanism

  Unfortunately, the undo and redo mechanisms does not work for task lists (with the widgets and tags) and will lead to unexpected behavior. This is due to the hard coded and not very flexible way the undo mechanism works in Tomboy, that is not really accessible from within Addins.
  
  As a temporary solution we started implementing methods that make it impossible to undo things, where unexpected behavior would be the result (for example, deleting a task in the Buffer as a result of an undo, but keeping the task in the internal data structures). However, this is not yet complete.

\item Insertion of a task list just above an other

  The insertion of a task list just above an other task list does not work correctly.

\item Strike-through update
  
  The strike-through update is not done when (un-)marking a task as not done.
  This glitch was introduced while applying maintenance changes and not discovered until after the submission.

\item Window size keeps increasing

  The initial goal of making the window of a note a bit wider so the TaskManager menu will be shown by default, led to the bug that this increased width would be saved. This introduced the problem that the size would be increased further at every new start up of Tomboy.

\end{itemize}